Results Analysis

### 2024-06-04 analysis/resultsAnalysis.Rmd
Plot changes
Superficial alterations to plots

quantLength %>%  
 ggplot(mapping = aes(x = ppc_name, y = Length, colour = sample_id)) +
 geom_violin(
    color = "black",
    fill = "lightblue",
    alpha = 0.5
 ) +
 geom_jitter(width = 0.1,
             alpha = 0.8) + 
 scale_fill_brewer(palette = "Set2") +
 scale_color_brewer(palette = "Set2") +
 coord_flip() +
 theme_bw() +
 labs(title = "All stated quantitative length Limits", x = "Post-publication critique type", y = "Length limits (words)")

```
Boxplot of quantitative time limits
```{r}
quantTime <- d_journals %>%
 select(c(sample_id, ppc_name, ppc_time)) %>%
 filter(!is.na(ppc_time),
         ppc_time != "NOT STATED",
         ppc_time != "Qualitative") %>%
 mutate(Time = as.numeric(ppc_time))

quantTime %>%  
 ggplot(mapping = aes(x = ppc_name, y = Time, colour = sample_id)) +
 geom_boxplot(
    color = "black",
    fill = "lightblue",
    alpha = 0.5
 ) +
 geom_jitter(width = 0.2) + 
 scale_fill_brewer(palette = "Set2") +
 scale_color_brewer(palette = "Set2") +
 coord_flip() +
 theme_bw() +
 labs(title = "All stated quantitative time limits", x = "Post-publication critique type", y = "Time limits (weeks)")
```
### *Post-Publication Critique Policy and Restriction Statements in Prominent Psychology Journals*

@@

#ggsave("ProminentJournalPolicies.png", plot = last_plot(), device = "png")
```

@@

#ggsave("RandomJournalPolicies.png", plot = last_plot(), device = "png")
```

>>>>

quantLength %>%  
 ggplot(mapping = aes(x = ppc_name, y = Length, colour = sample_id)) +
 geom_boxplot(
    color = "black",
    fill = "lightblue",
    alpha = 0.4
 ) +
 geom_jitter(width = 0.3,
             alpha = 0.8,
             size = 2) + 
 scale_color_manual(values = c("prominent" =  "#ff6347", 
                              "random" =   "#8db600",
                              "both" = "#000080")
                    ) +
 coord_flip() +
 scale_y_continuous(n.breaks = 8) +
 theme_bw() +
 theme(axis.text.y = element_text(angle = 90, hjust = 0.5)) +
 labs(title = "All stated quantitative length limits", 
      x = "Post-publication critique type", 
      y = "Length limits (words)", 
      colour = "Sample")

ggsave("lengthLimits.png", plot = last_plot(), device = "png")
```
Boxplot of quantitative time limits
```{r}
quantTime <- d_journals %>%
 select(c(sample_id, ppc_name, ppc_time)) %>%
 filter(!is.na(ppc_time),
         ppc_time != "NOT STATED",
         ppc_time != "Qualitative") %>%
 mutate(Time = as.numeric(ppc_time))

quantTime %>%  
 ggplot(mapping = aes(x = ppc_name, y = Time, colour = sample_id)) +
 geom_boxplot(
    color = "black",
    fill = "lightblue",
    alpha = 0.4
 ) +
 geom_jitter(width = 0.2,
             alpha = 0.8,
             size = 2) + 
 scale_color_manual(values = c("prominent" =  "#ff6347", 
                              "random" =   "#8db600",
                              "both" = "#000080")
                    ) +
 coord_flip() +
 theme_bw() +
 theme(axis.text.y = element_text(angle = 90, hjust = 0.5)) +
 labs(title = "All stated quantitative time limits", 
      x = "Post-publication critique type", 
      y = "Time limits (weeks)", 
      colour = "Sample")

ggsave("timeLimits.png", plot = last_plot(), device = "png")
```
### *Post-Publication Critique Policy and Restriction Statements in Prominent Psychology Journals*

@@

ggsave("ProminentJournalPolicies.png", plot = last_plot(), device = "png")
```

@@

ggsave("RandomJournalPolicies.png", plot = last_plot(), device = "png")
```
